Chile Gaps Time

### 2020-01-16 paper.Rmd
ad original bib

---
title: 'Chile Gaps Time'
author: ""
output:
    html_document:
        smart: false
        toc: true
        number_sections: true
bibliography: "input/bib/Link to My Library.bib"
csl: "input/bib/apa6.csl"
---

>>>>

---
title: 'Chile Gaps Time'
author: ""
output:
    html_document:
        smart: false
        toc: true
        number_sections: true
bibliography: "input/bib/My Library.bib"
csl: "input/bib/apa6.csl"
---
